Adaptive broadcast tree for multicores

### 2013-05-02 paper.tex
Clean-up of node and link characteristics

Every node (i.e.\ core) in the system has characteristics associated
with it:

\begin{description}
\item[synchrony] Parts of a multicore machine are synchronous. Hence,
  one characteristic of a node is an identifier for the synchrony
  cluster of a node.
\item[send time $t_{send}$] Time required to send a message, i.e.\ marshalling
  and queuing the message
\item[receive $t_{recv}$] Time required to receive a message, i.e.\
  dequeuing, unmarshalling and demultiplexing a channel.
\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
\end{description}

@@

\begin{description}
\item[latency] (quantitative) between each pair of nodes (per-edge)
\item[breakdown] (quantitative) of message send cost:
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node)
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): 
  multicore interconnect networks often are
\end{description}

@@

It is doubtful that a key-value store as a backend for synchronization
primitives makes sense. As we want to show efficiency, we probably
rather want to implement new synchronization algorithms from scratch.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barriers}

>>>>

Every node (i.e.\ core) in the system has characteristics associated
with it.

\begin{description}
\item[synchrony] Parts of a multicore machine are synchronous. Hence,
  one characteristic of a node is an identifier for the synchrony
  cluster of a node.
\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
\end{description}

These are currently not encoded in the model. The send and receive
cost are in part node specific. The faster a core is, the faster it
can to the multiplexing and marshalling. However, they are also link
dependent, so we view them as link characteristics.

@@

\begin{description}
\item[breakdown] (quantitative) of message send cost:
  dominating propagation time vs.\ dominating send and receive time on
  multicores (per-node). Our model is currently limited to only the
  breakdown of the cost for sending messages.
\item[latency] (quantitative) between each pair of nodes (per-edge)
\item[bounded delivery]
\item[reliability] (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): 
  multicore interconnect networks often are
\end{description}

@@

It is doubtful that a key-value store as a backend for synchronization
primitives as we want to show efficiency rather than ease of use and
flexibility. We probably rather want to implement new synchronization
algorithms from scratch. See Section~\ref{barriers} for ideas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barriers}
\label{barriers}
